Tutorial 1b

### 2025-07-13 Tutorial_1b.Rmd
update Figures Tutorial 1b

Tutorial 1b illustrates how to use functional programming to set up life tables, and plot the discrete-time hazard, survivor, and conditional accuracy functions, for the data of Experiment 1 of @panisWhatShapingRT2016 when there are TWO independent variables (here: mask type and prime type).

>>>>

Tutorial 1b illustrates how to use functional programming to set up life tables, and plot the discrete-time hazard, survivor, and conditional accuracy functions, for the data of Experiment 1 of @panisWhatShapingRT2016 when there are two independent variables (here: mask type and prime type).
